SoK: Transparent Dishonesty. Front-running attacks on Blockchain.

### 2018-12-06 auditing/Latex/main.tex
ack
changes

\section{Acknowledgements}

The authors thank the Autorit\'e des March\'es Financiers (AMF) for sponsoring this research through the Education and Good Governance Fund (EGGF).

>>>>

\subsection*{Acknowledgements}

The authors thank the Autorit\'e des March\'es Financiers (AMF) for sponsoring this research through the Education and Good Governance Fund (EGGF). Additionally the first author acknowledges funding from SSHRC, the second author from the Manulife Professorship in Financial Planning at JMSB, and the fourth author from an NSERC Discovery Grant. The paper was greatly improved by feedback from \ldots TBD. The information, opinions and advice presented in this paper are the sole responsibility of the authors.

% = = = = = Bibliography = = = = =

### 2018-12-06 frontrunning/Latex/sections/paper.tex
changes

We encounter a number of main approaches to mitigate front-running attacks on blockchains: we summerize the main approaches.

one is to design a blockchain that is front-run resistant, and the other to design the application logic in a way that front-running is not profitable. This can be done in addition to any legal remedies that might be enforceable (See Appendix ~\ref{app:traditionalprevention}). We note, but consider out-of-scope, approaches that introduce trusted parties to centralize time-sensitive functionalities (\eg exchanges \textit{EtherDelta} and \textit{0xProject} use off-chain order books~\cite{warren20170x,0xfrontrunning:online}).

In this section, we describe the potential solutions using which, one can design and implement a decentralized application that is resistant to front-running. Note that, the existing technical difficulties make these solutions hard to achieve as it requires designers to test edge case scenarios.

@@

\paragraph{Design Decision \#1: Fixed Transaction Ordering.} da Silva~\etal~\cite{fixedordering2018silva} proposes an algorithm, known as Fixed Transaction Ordering and Admission (FTOA), in the consensus protocol that enforces the order of the transactions in the mined blocks, using logical timestamps in a Byzantine setting, to eliminate transaction reordering by miners. This is a theoretical solution and is not trivial to implement in the current Byzantine consensus protocols. An implementation of fixed transaction ordering is Canonical Transaction Ordering Rule (CTOR) introduced in November 2018 fork of Bitcoin cash, which indicates an order in which blocks are valid based on the order of the transactions in them; coinbase first, then ascending lexicographic order based on transaction hash~\cite{bitcoinABC2018CTOR}. This solution can potentially mitigate the re-ordering attack by miners, however it does not prevent it fully. 
%NOTE: the two solutions above are both on the transaction ordering, however Silva's solution requires a logical timestamp, and CTOR uses sorting based on transaction hash.

@@

>>>>

As we studied front-running attacks on blockchain, we also encountered a number of ways of preventing, detecting, or mitigating front-running attacks. Instead of providing the details of exact solutions which will change over time, we extract the main principles or primitives that address the attack. A particular system may implement more in a layered mitigation approach.

We classify the mitigations into three main categories. In the first category, the blockchain removes the miner's ability to arbitrarily order transactions and tries to enforce some ordering, or queue, for the transactions. In the second category, cryptographic techniques are used to limit the visibility of transactions, giving the potential front-running less information to base their strategy on. In the final category, dapps are designed from the bottom-up to remove the importance of transaction ordering or time in their operations.

We also note that for dapps that are legally well-formed (\eg with identified parties and a clear jurisdiction), front-running attacks can violate laws, which is its own deterrent. We do not discuss this further here; see Appendix ~\ref{app:traditionalprevention}.

@@

% Jeremy: to do

Transaction chaining -> resolve conflicts -> topological order/sort (also consider total order) -> cf UTXOs

FIFO -> consensus on FI -> possible in theory
-> could be solved with TTP -> censorship still possible (completeness issue)

FI_O -> FIRO -> deterministic random order -> manipulatable (malleability in the collection and your own items in the collection and maybe and other items in the collection) -> CTOR

%\paragraph{Design Decision \#1: Fixed Transaction Ordering.} da Silva~\etal~\cite{fixedordering2018silva} proposes an algorithm, known as Fixed Transaction Ordering and Admission (FTOA), in the consensus protocol that enforces the order of the transactions in the mined blocks, using logical timestamps in a Byzantine setting, to eliminate transaction reordering by miners. This is a theoretical solution and is not trivial to implement in the current Byzantine consensus protocols.

An implementation of fixed transaction ordering is Canonical Transaction Ordering Rule (CTOR) introduced in November 2018 fork of Bitcoin cash, which indicates an order in which blocks are valid based on the order of the transactions in them; coinbase first, then ascending lexicographic order based on transaction hash~\cite{bitcoinABC2018CTOR}. This solution can potentially mitigate the re-ordering attack by miners, however it does not prevent it fully. 
%NOTE: the two solutions above are both on the transaction ordering, however Silva's solution requires a logical timestamp, and CTOR uses sorting based on transaction hash.

@@

We note, but consider out-of-scope, approaches that introduce trusted parties to centralize time-sensitive functionalities (\eg exchanges \textit{EtherDelta} and \textit{0xProject} use off-chain order books~\cite{warren20170x,0xfrontrunning:online}).
